Demography and linked selection in wild and domesticated maize

### 2015-08-26 manuscript.tex
minor edits

\section{Results}
\subsection{Patterns of diversity differ between genic and  non-genic regions of the genome}
To investigate how demography and linked selection have shaped patterns of diversity in maize and teosinte, we reanalyzed data from 23 maize and 13 teosinte genomes from the maize HapMap 2 project \cite{chia2012}.
We find broad differences in genic and non-genic diversity consistent with earlier results  \cite{hufford2012} (Figure \ref{fig:diversity}).  
In maize, mean pairwise diversity ($\pi$) within genes was significantly lower than at positions at least 5 kb away from genes (0.00668 vs 0.00691, $p<2\times 10^{-44}$). 
Diversity differences in teosinte are even more pronounced (0.0088 vs. 0.0115, $p\approx 0$). 
Differences were also apparent in the site frequency spectrum, with mean Tajima's D positive in genic regions in both maize (0.4) and teosinte (0.013) but negative outside of genes (-0.087 in maize and -0.25 in teosinte, $p\approx 0$ for both comparisons).
These observations suggest that diversity in genes is not evolving neutrally, but instead is reduced by the impacts of selection on linked sites.

\begin{figure}
\begin{center}
  \includegraphics[width=.5\textwidth] {FigsAndFiles/Pi_and_Tajima.png}
\end{center}
\caption{Pairwise diversity (Pi) and Tajimas D were calculated inside and outside of genes for maize and teosinte. In both taxa, a dearth of rare alleles was observed within genes relative to outside of genes, which led to higher values of Tajima's D outside of genes than inside.{\bf A:} Mean and standard deviation of pi for 1 kb genic and non-genic windows of maize; {\bf B:} Mean and standard deviation of pi for 1 kb genic and non-genic windows of teosinte  {\bf C:} Histogram of Tajima's D in 1 kb windows in maize; {\bf D:} Histogram of Tajima's D in 1 kb windows in teosinte.  \label{fig:diversity} }
\end{figure}

@@

\begin{figure}
%\vspace*{.05in}
\centering
\includegraphics[width=.4\textwidth]{FigsAndFiles/DomesticationModel/domesticationModel.pdf}
\caption{Parameter estimates for a simple bottleneck model of maize domestication. See methods for details. \label{fig:bottleneck} }
\end{figure}

>>>>

\section{Results}
\subsection{Patterns of diversity differ between genic and  non-genic regions of the genome}
To investigate how demography and linked selection have shaped patterns of diversity in maize and teosinte, we reanalyzed data from 23 maize and 13 teosinte genomes from the maize HapMap 2 project \cite{chia2012}.
We find broad differences in genic and non-genic diversity consistent with earlier results  \cite{hufford2012} (Figure \ref{fig:diversity}\jri{pi graph should use greek letter $\pi$}).  
In maize, mean pairwise diversity ($\pi$) within genes was significantly lower than at positions at least 5 kb away from genes (0.00668 vs 0.00691, $p<2\times 10^{-44}$). 
Diversity differences in teosinte are even more pronounced (0.0088 vs. 0.0115, $p\approx 0$). 
Differences were also apparent in the site frequency spectrum, with mean Tajima's D positive in genic regions in both maize (0.4) and teosinte (0.013) but negative outside of genes (-0.087 in maize and -0.25 in teosinte, $p\approx 0$ for both comparisons).
These observations suggest that diversity in genes is not evolving neutrally, but instead is reduced by the impacts of selection on linked sites.

\begin{figure}
\begin{center}
  \includegraphics[width=.4\textwidth] {FigsAndFiles/Pi_and_Tajima.png}
\end{center}
\caption{Pairwise diversity $\pi$ (A,B) and Tajimas D (C,D) in 1kb windows from genic and nongenic regions of maize (A,C) and teosinte (B,D). Shown in A and B are means and one standard deviation.   \label{fig:diversity} }
\end{figure}

@@

\begin{figure*}
%\vspace*{.05in}
\centering
\includegraphics[width=.4\textwidth]{FigsAndFiles/DomesticationModel/domesticationModel.pdf}
\caption{Parameter estimates for a simple bottleneck model of maize domestication. See methods for details. \label{fig:bottleneck} }
\end{figure*}
